thesis2024

### 2025-05-02 article3.qmd
Macbook session. Tests to latex chapter structure 01

hypotheses <- readr::read_csv(here::here('analysis/data/tables/hypotheses_short.csv'))

@@

knitr::include_graphics(here::here("analysis/figures/VB_map.png"))

@@

knitr::include_graphics(here::here("analysis/figures/types_short.png"))

@@

# Reading the datasets
## Technological data
gravettian_tech <- read_csv(here::here('analysis/data/raw_data/VBT_6_7_JB.csv'))
proto_tech <- read_csv(here::here('analysis/data/raw_data/VBT_4E_5_JB.csv'))
solutrean_JC <- read_csv(here::here('analysis/data/raw_data/VBR_ABC_JC.csv'))
solutrean_points <- read_csv(here::here('analysis/data/raw_data/shelter_points_JC.csv'))

## RM data
shelter_RM <- read_csv(here::here('analysis/data/raw_data/MACRO_IND_SHELTER.csv')) # Shelter RM analysis
terrace_RM <- read_csv(here::here('analysis/data/raw_data/MACRO_IND_TERRACE.csv')) # Terrace RM analysis

## Context data
context <- read_csv(here::here('analysis/data/raw_data/VB_Terrace_context.csv')) # Terrace Field DB - lithic artefact info
xyz <- read_csv(here::here('analysis/data/raw_data/VB_Terrace_xyz.csv')) # Terrace Field DB - just coordinates

@@

p_results <- readr::read_csv(here::here('analysis/data/tables/results_sum.csv'))

>>>>

hypotheses <- readr::read_csv(here::here('data/raw_data_from-stone-to-tool/hypotheses_short.csv'))

@@

knitr::include_graphics(here::here("figures/from-stone-to-tool/VB_map.png"))

@@

knitr::include_graphics(here::here("figures/from-stone-to-tool/types_short.png"))

@@

# Reading the datasets
## Technological data
gravettian_tech <- read_csv(here::here('data/raw_data_from-stone-to-tool/VBT_6_7_JB.csv'))
proto_tech <- read_csv(here::here('data/raw_data_from-stone-to-tool/VBT_4E_5_JB.csv'))
solutrean_JC <- read_csv(here::here('data/raw_data_from-stone-to-tool/VBR_ABC_JC.csv'))
solutrean_points <- read_csv(here::here('data/raw_data_from-stone-to-tool/shelter_points_JC.csv'))

## RM data
shelter_RM <- read_csv(here::here('data/raw_data_withinandbeyond/MACRO_IND_SHELTER.csv')) # Shelter RM analysis
terrace_RM <- read_csv(here::here('data/raw_data_withinandbeyond/MACRO_IND_TERRACE.csv')) # Terrace RM analysis

## Context data
context <- read_csv(here::here('data/raw_data_withinandbeyond/VB_Terrace_context.csv')) # Terrace Field DB - lithic artefact info
xyz <- read_csv(here::here('data/raw_data_withinandbeyond/VB_Terrace_xyz.csv')) # Terrace Field DB - just coordinates

@@

p_results <- readr::read_csv(here::here('data/raw_data_from-stone-to-tool/results_sum.csv'))
